---
title: "Lab 9"
author: "Shiyu Yang"
date: "01/04/2021"
output: html_document
---

## Neural networks (seeds data)

seeds data set from UCI repository1

Explore the data.

Measurements of geometrical properties of kernels belonging to three different varieties of wheat. A soft X-ray technique and GRAINS package were used to construct all seven, real-valued attributes.

```{r}
library(tidyverse)
seeds <- read.table(
  "https://archive.ics.uci.edu/ml/machine-learning-databases/00236/seeds_dataset.txt"
  )
colnames(seeds) <- c("area", 
                     "perimeter", 
                     "compactness", 
                     "length_of_kernel", 
                     "width_of_kernel",
                     "asy_coeff", 
                     "length_of_kernel_groove", 
                     "Class")
summary(seeds)
cor(dplyr::select(seeds, -Class))

```

Print tidy seeds data set.
```{r}
library(dplyr)
dim(seeds)
knitr::kable(head(seeds)) %>%
  kable_styling(latex_options="scale_down")

```

We scale the predictors.
```{r}
x <- seeds %>%
  dplyr::select(-Class) %>%
  scale()
```

We split 75%/25% training/test set.
```{r}
set.seed(1)

seeds_train_index <- seeds %>%
  mutate(ind = 1:nrow(seeds)) %>%
  group_by(Class) %>%
  mutate(n = n()) %>%
  sample_frac(size = .75, weight = n) %>%
  ungroup() %>%
  pull(ind)
```

We create binary output units yk,k=1,2,3 using class.ind().
```{r}
library(nnet)
class_labels <- pull(seeds, Class) %>% 
  class.ind() 
knitr::kable(head(class_labels)) %>%
  kable_styling(latex_options="scale_down")
```

Create predictor matrix for training/test set and output for training/test set.
```{r}
seeds_train <- x[seeds_train_index, ]
train_class <- class_labels[seeds_train_index,]
seeds_test <- x[-seeds_train_index, ] 
test_class <- class_labels[-seeds_train_index,]
```

Let’s look at the help page for nnet().
Let’s tune size = number of units in the hidden layer and decay = weight decay parameter.
```{r}
nn_seeds <- nnet(
  x = seeds_train, 
  y = train_class, 
  size = 4, 
  decay = 0, 
  softmax = TRUE,
  maxit=500
  )

```

Compute test error for NN with size = 4 and decay = 0.
```{r}
nn_pred <- predict(nn_seeds, seeds_test, 
                   type="class")

tab_seeds <- table(slice(
  seeds, 
  -seeds_train_index) %>% pull(Class), 
  nn_pred)

1-sum(diag(tab_seeds))/sum(tab_seeds)
```

